Exploration of the MIRT solutions

### 2024-01-16 notebooks/Mirt_solution_exploration.Rmd
Adds necessary packages
Corrects notebook output

---
title: 'Exploration of the MIRT solutions'
output:
  html_document: 
    df_print:        paged
    code_folding:    hide
    toc:             yes
    toc_float:       yes
editor_options: 
  chunk_output_type: console
---

```{r setup}
library(knitr)
library(mirt)

@@

cov_matrix <- cov_pars[c('COV_11', 'COV_21', 'COV_21', 'COV_22')] |>
  matrix(nrow = 2)
```

@@

```{r compute-fscores}
scores <- fscores(mod2, response.pattern = LSAT7[, 1:5])
```

>>>>

---
title: 'Exploration of the MIRT solutions'
output:
  html_document: 
    df_print:        paged
    code_folding:    show
    toc:             yes
    toc_float:       yes
editor_options: 
  chunk_output_type: console
---

```{r setup}
library(knitr)
library(mirt)
library(tidyverse)

@@

cov_matrix <- cov_pars[c('COV_11', 'COV_21', 'COV_21', 'COV_22')] |>
  matrix(nrow = 2)

item_pars
```

@@

```{r compute-fscores}
fscores(mod2, response.pattern = LSAT7[, 1:5])
```
